Performance of two different ontological and data access methods

### 2015-03-05 cold2014/magnus.tex
Rewrite the text around figures in discussion
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1044 43ef1190-90fd-4dd7-a769-d0121f02b80e

In the Figure~\ref{3factorGraph} we can see that only one significant
effects, the O factor. We saw in Table~\ref{3factorEffect} that the
Configuration Ontology was almost two seconds slower than the VSO/COO
runs.  Three out of four CO runs kept the response time around two
seconds, but one run had to use approximately 3.5 seconds which
resulted in an average run time of $\approx2.3$ seconds.  In a study
done to research the amount of time a user would be willing to wait,
they found out that the tolerable waiting time for any information
retrieval was approximately 2 seconds.~\cite{waitTime} This means that
with three factors we were still within the time frame for a good user
experience.

@@

In Figure~\ref{10factorGraph} we can see the results from this
experiment. In Table
\ref{10factorEffect} we see the top twenty absolute effects and
similar to all the other experiments, O is on top of the list. The
average response time of a run done against CO was $\approx58.5$
seconds while a run against VSO/COO had an average response time of
$\approx0.3$ seconds.  This corresponds with the absolute effect of
the O factor to be 58 seconds.

>>>>

We noted that the O factor was the only significant factor. 
We saw in Table~\ref{3factorEffect} that the
Configuration Ontology was almost two seconds slower than the VSO/COO
runs.  Three out of four CO runs kept the response time around two
seconds, but one run had to use approximately 3.5 seconds which
resulted in an average run time of $\approx2.3$ seconds.  In a study
done to research the amount of time a user would be willing to wait,
they found out that the tolerable waiting time for any information
retrieval was approximately 2 seconds.~\cite{waitTime} This means that
with three factors we were still within the time frame for a good user
experience.

@@

In Table \ref{10factorEffect} we see the top twenty absolute effects
and similar to all the other experiments, O is on top of the list. The
average response time of a run done against CO was $\approx58.5$
seconds while a run against VSO/COO had an average response time of
$\approx0.3$ seconds.  This corresponds with the absolute effect of
the O factor to be 58 seconds.
